\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data


\firstname{Rodrigo}
\familyname{Villablanca}
\title{Ingeniero Civil en Computación}
\address{Papudo 3134}{Maipú}
\mobile{+56 974733360}
%\phone{(56)2 9482130}
\email{villa061004@gmail.com}               
%\photo[64pt]{ariel.eps}                         


% to show numerical labels in the bibliography; only useful if you make citations in your resume
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle


\section{Información Personal}

\cventry{Nombre Completo}{Rodrigo Antonio Villablanca Vásquez}{}{}{}{}

\cventry{R..U.T.}{16.089.456-3}{}{}{}{}

\cventry{Fecha de Nacimiento}{10 de Julio de 1986}{}{}{}{}

\cventry{Estado Civil}{Casado}{}{}{}{}

\cventry{Nacionalidad}{Chileno}{}{}{}{}

\section{Formación académica}

\cventry{1992-1998}{Ingeniero Civil en Computación}{Titulado en la Facultad de Ingeniería de la \textbf{Universidad Tecnológica Metropolitana de Chile}}{}{}{}

\cventry{1988-1991}{1ro. a 4to. Medio.}{Liceo Carolina Llona de Cuevas}{}{}{}

\section{Experiencia Profesional}

\cventry{2014-Presente}{Ingeniería y Arquitectura de Software}{KDU Ingeniería}{Trabajo como Desarrollador de Software Senior para diversos clientes, entre ellos Falabella, Transbank, Travelclub, Copec, etc. Formo parte del equipo de Arguitectura para las definiciones de tecnologías a usar e infraestructura de aplicaciones. Formo parte de un equipo multidisciplinario que trabaja con SCRUM con el cargo de Arguitecto de Software en Transbank}{}{}{}

\cventry{2011-2013}{Ingeniero de Software}{Experti (ex Orange People)}{Me integré al equipo de desarrollo de Webpay, un plataforma de pago online usado en Chile para todas las transacciones de e-commerce online. Otros desarrollos estuvieron relacionados con agencias de seguros, medios de pago y sistemas de integración con GDS (Global Distribution System).}{}{}{}

\closesection{}
\pagebreak

\section{Conocimientos}
\cvcomputer{SO}{GNU/Linux (Debian, Ubuntu, Arch), Microsoft Windows}{Admin.}{Apache Web Server, Nginx, Apache Tomcat, FTP servers, SSH, HTTP proxys}
\cvcomputer{DB}{MySQL, PostgreSQL, Oracle, HSQL, Microsoft SQL Server}{}{}
\cvcomputer{Java}{JSE/JEE, Spring Framework/Boot, WebServices SOAP/Rest, JPA/Mongo, JSF/JSP/Struts, JMS, Tomcat/Weblogic, Maven/Ant, Logging/log4j/slf4j}{Golang}{Gorilla Mux, Viper, GinFramework, Gitea/Gogs, Standard Library/http}
\cvcomputer{Frontend}{AngularJS, Angular 2+, html/css/javascript, Vue}{Other}{C/C++, Python}
\cvcomputer{DevOps}{Docker, Linux/ssh, Shell Script/Bash, Apache HTTP/Nginx, Ubuntu/Debian/Arch, git/svn, Deployment Process, Kubernetes, DigitalOcean}{}{}

\section{Idiomas}
\cvlanguage{Español}{Nativo}{}
\cvlanguage{Inglés}{Nivel intermedio}{}

\end{document}
